### 2018-10-09 papers/journal/experiments.tex
restructure experiments

\begin{enumerate}
  \item CBMC: \\
The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
%
Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
CBMC allows the depth of model to be incrementally increased to any desired value.

@@

CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification. Besides using MiniSat as a default SAT solver for our model,
		we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
%		
MiniSat performed satisfactorily in comparison to other SAT solvers.
\item Z3: \\
	We have implemented the encodings for each variants using the python interface of Z3 in a tool (MAA). 
%
Our tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model ( a satisfying assignment that respects the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and presents a visual output to the user in form of annotated graph. 
%
We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.

\item DEPQBF: \\
We have implemented the encodings in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS. 
%
The tool can not only synthesize the above-discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. 
%
Since some of the formulas involve alternation of quantifiers over
Boolean variables Z3 is not a suitable choice for those examples.
%
We translate the formulas created by Z3 tool into a standard
QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
%
Our tool includes about 7000 lines of code.

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

@@

\end{enumerate}

>>>>

We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings. All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
\subsection{SATVTS (Bounded model checker based tool)} 
The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
%
Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
CBMC allows the depth of model to be incrementally increased to any desired value.

@@

CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification. Besides using MiniSat as a default SAT solver for our model, we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
%		
MiniSat performed satisfactorily in comparison to other SAT solvers.

\subsection{SMTVTS/pyVTS (SMT based tool)}
	We have implemented the encodings for each variants using the python interface of Z3 in a tool (MAA). 
%
Our tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model ( a satisfying assignment that respects the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and presents a visual output to the user in form of annotated graph. 
%
We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.

\subsection{SynthVTS (QBF based synthesis tool)} 
We have implemented the encodings in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS. 
%
The tool can not only synthesize the above-discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. 
%
Since some of the formulas involve alternation of quantifiers over
Boolean variables Z3 is not a suitable choice for those examples.
%
We translate the formulas created by Z3 tool into a standard
QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
%
Our tool includes about 7000 lines of code.

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

@@
